### 2022-09-12 Bloods Data Sheet.Rmd
Calculating percentage change for electrolytes

#calculating Percentage Change
##CK
```{r}
CK_PCHANGE <- main_df2%>%
  summarySE(measurevar = "cal_CK", groupvar =c("Session", "Time_Point","Participant"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)

@@

```{r}
names(main_df2)
```

@@

>>>>

#Calculating Percentage Change
##CK
```{r}
CK_PCHANGE <- main_df2%>%
  summarySE(measurevar = "cal_CK", groupvar =c("Session", "Time_Point","Participant"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)

@@

@@

##Sodium
```{r}
sodium_PCHANGE <- main_df2%>%
  summarySE(measurevar = "cal_Na", groupvar =c("Session", "Time_Point","Participant"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)

```{r}
write.csv(sodium_PCHANGE,"C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\sodium_PCHANGE (12-09-2022a).csv",row.names = FALSE)

sodium_PCHANGE_CL <- read.csv("C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\Percentage Change\\sodium_PCHANGE (12-09-2022).csv")
```

```{r}
sodium_PCHANGE_CL<-sodium_PCHANGE_CL%>%
  mutate(P_CHANGE = ((POST_EXERCISE-PRE_EXERCISE)/PRE_EXERCISE)*100)

sodium_PCHANGE_CL_SUM <-sodium_PCHANGE_CL%>% 
summarySE(measurevar = "P_CHANGE", groupvar =c("Time_Point", "BFR", "speed", "Session"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)

##Potassium
```{r}
sodium_PCHANGE <- main_df2%>%
  summarySE(measurevar = "cal_K", groupvar =c("Session", "Speed", "BFR", "Time_Point","Participant"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)

```{r}
write.csv(sodium_PCHANGE,"C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\Percentage Change\\potassium_PCHANGE (12-09-2022).csv",row.names = FALSE)

potassium_PCHANGE_CL <- read.csv("C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\Percentage Change\\potassium_PCHANGE (12-09-2022).csv")
```

```{r}
potassium_PCHANGE_CL<-potassium_PCHANGE_CL%>%
  mutate(P_CHANGE = ((POST_EXERCISE-PRE_EXERCISE)/PRE_EXERCISE)*100)

potassium_PCHANGE_CL_SUM <-potassium_PCHANGE_CL%>% 
summarySE(measurevar = "P_CHANGE", groupvar =c("Time_Point", "BFR", "Speed", "Session"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)

##Chloride
```{r}
chloride_PCHANGE <- main_df2%>%
  summarySE(measurevar = "cal_Cl", groupvar =c("Session", "Speed", "BFR", "Time_Point","Participant"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)

```{r}
write.csv(chloride_PCHANGE,"C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\Percentage Change\\chloride_PCHANGE (12-09-2022).csv",row.names = FALSE)

chloride_PCHANGE_CL <- read.csv("C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\Percentage Change\\chloride_PCHANGE (12-09-2022).csv")
```

```{r}
chloride_PCHANGE_CL<-chloride_PCHANGE_CL%>%
  mutate(P_CHANGE = ((POST_EXERCISE-PRE_EXERCISE)/PRE_EXERCISE)*100)

chloride_PCHANGE_CL_SUM <-chloride_PCHANGE_CL%>% 
summarySE(measurevar = "P_CHANGE", groupvar =c("Time_Point", "BFR", "Speed", "Session"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)
